|

### 2023-01-27 paper.Rmd
Fri Jan 27 17:00:07 CET 2023: update-remote.sh

---
title: |
  <center>Pre-Trained Denoising Autoencoders Long Short-Term Memory Networks as probabilistic Models for Estimation of Distribution Genetic Programming</center>
  <center>Master Thesis - M.Sc. Business Education</center>
  <center>--------------------------------------------------------</center>
  <center>Student: Roman Höhn</center>
  <center>Date of Birth: 1991-04-14</center>
  <center>Place of Birth: Wiesbaden, Hesse</center>
  <center>Student ID: 2712497</center>
  <center>Supervisor: David Wittenberg</center>
  <center>--------------------------------------------------------</center>
  <center>Master Thesis</center>
  <center>FB 03: Chair of Business Administration and Computer Science</center>
  <center>Johannes Gutenberg University Mainz</center>
  |
date: "Date of Submission: `r Sys.Date()`"
output:
  bookdown::pdf_document2:
    keep_tex: true
    extra_dependencies: ["float"]
    fig_caption: yes
    number_sections: true
    includes:
      in_header: [header_files/settings.tex]
indent: false
fontsize: 11pt
bibliography: ./ref/ref.bib
link-citations: true
fig.width: 4in
fig.height: 3in
csl: csl/association-for-computing-machinery.csl
#csl: csl/harvard-cite-them-right.csl
#csl: csl/springer-science-reviews.csl
include-before: '`\thispagestyle{empty} \newpage{}`{=latex}'
---

@@

```{bash recompile-results, echo=TRUE, eval=FALSE, include=FALSE}

>>>>

---
title: |
  <center>Pre-Trained Denoising Autoencoders Long Short-Term Memory Networks as probabilistic Models for Estimation of Distribution Genetic Programming</center>
  <center>Master Thesis - M.Sc. Business Education</center>
  <center>--------------------------------------------------------</center>
  <center>Student: Roman Höhn</center>
  <center>Date of Birth: 1991-04-14</center>
  <center>Place of Birth: Wiesbaden, Hesse</center>
  <center>Student ID: 2712497</center>
  <center>Supervisor: David Wittenberg</center>
  <center>--------------------------------------------------------</center>
  <center>Master Thesis</center>
  <center>FB 03: Chair of Business Administration and Computer Science</center>
  <center>Johannes Gutenberg University Mainz</center>
  |
date: "Date of Submission: `r Sys.Date()`"
output:
  bookdown::pdf_document2:
    keep_tex: true
    extra_dependencies: ["float"]
    fig_caption: yes
    number_sections: true
    toc_depth: 3
    includes:
      in_header: [header_files/settings.tex]
indent: false
fontsize: 11pt
bibliography: ./ref/ref.bib
link-citations: true
fig.width: 4in
fig.height: 3in
csl: csl/association-for-computing-machinery.csl
#csl: csl/harvard-cite-them-right.csl
#csl: csl/springer-science-reviews.csl
include-before: '`\thispagestyle{empty} \newpage{}`{=latex}'
---

@@

```{bash recompile-results, echo=TRUE, eval=TRUE, include=FALSE}

### 2023-01-27 paper.tex
Fri Jan 27 17:00:07 CET 2023: update-remote.sh

{
\setcounter{tocdepth}{2}
\tableofcontents
}
\setcounter{page}{1}
\tableofcontents
\thispagestyle{empty}
\newpage
\listoftables
\listoffigures
\thispagestyle{empty}
\newpage

@@

Since previous work by {[}\protect\hyperlink{ref-dae-gp_2022_symreg}{17}{]} demonstrated that DAE-GP was capable of producing solutions that are much smaller in tree size that regular GP, I also studied the influence of pre-training on the size of solutions found by DAE-GP.

Since {[}\protect\hyperlink{ref-dae-gp_2022_symreg}{17}{]} shows, that DAE-GP finds higher quality that are also smaller in size than those found by average GP for a given number of 10.000 fitness evaluations, I also studied the differences in average solution size between pre-trained and regular DAE-GP. Figure \ref{fig:airfoil-size-combined-30gens} shows the median of both the average size of individuals inside the population as well as the size of the currently best performing solution inside the population. It can be observed that both DAE-GP variants strongly reduce the average solutions size already in the first generations and that the average solution size inside the population constantly stays at this very low level for the rest of the search.

>>>>

{
\setcounter{tocdepth}{3}
\tableofcontents
}
\setcounter{page}{1}
\tableofcontents
\thispagestyle{empty}
\newpage
\listoftables
\listoffigures
\thispagestyle{empty}
\newpage

@@

Since previous work by {[}\protect\hyperlink{ref-dae-gp_2022_symreg}{17}{]} demonstrated that DAE-GP, for a given number of 10.000 fitness evaluations, was capable of producing solutions that are much smaller in tree size that regular GP, I also studied the influence of pre-training on the size of solutions found by DAE-GP. Figure \ref{fig:airfoil-size-combined-30gens} shows the median of both the average size of individuals inside the population as well as the size of the currently best performing solution inside the population. It can be observed that both DAE-GP variants strongly reduce the average solutions size already in the first generations and that the average solution size inside the population constantly stays at this very low level for the rest of the search.
